{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-22 documents/background.tex
why's fdtd broken?
Coplanar exposure cell working
Delay line functioning great

@@

>>>>

suggestive, especially because a model organism

@@

The field strengths are high enough to lead to Townsend breakdowns in air (if the duration is longer than the formative lag). In some sense, we are concerned with field magn

Dielectric measurements on different proteins demonstrate that the slowest relaxation

The very high voltage means that low-sensitivity diagnostics, like lithium niobate optical probes. Not having a suitable optical bench, an electron-beam probe, similar to a streak camera, itself similar in principle to scan-conversion digitizer tubes in Tek SCD and 7912 series transient digitizers.

If a low voltage sensitivity is required, and because modern high-pixel-density CMOS sensors allow the required deflection and the entire structure to be minimized, these are simple to design and inexpensive (much of the complexity being in the slow-wave or travelling-wave structure which is usually required to match the signal velocity to the - slowing down light without affecting its properties or drawing power is an extremely difficult problem) and can offer sample rates in the terasamples/s and analog bandwidths , albeit with low vertical resolution.

original von Ardenne
